### 2013-08-31 Tex/chapters/results.tex
fehlende Klammer korrigiert
Rechtschreib- und Kommafehler
außerdem kleiner Formulierungsverbesserungen

            rounded up and are determined as the maximum over all \(\sigma\).

@@

    are omitted in the following for the sake of simplicity, so that the

@@

    error estimate can be achieved by simple bootstrapping. Nevertheless one has

@@

    by gnuplot. Gnuplot is an open source plotting program, used for all plots
    and fits in this thesis \footnote{\url{http://gnuplot.info/}.}.

\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
\label{ssec:results:autocorr}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) is given to illustrate the benefits
    of the used Wolff cluster algorithm.\\
    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at
    \(\sigma=0\) is plotted. Note that these are the unrounded values
    of Tab.\ \ref{tab:tauAndTeq}.
    \begin{figure}[htbp]
        \centering
        \subfigure[in Dependence on the Temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in Dependence on the System Size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The Autocorrelation Time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$. Plotted on
                double logarithmic axis with a power law fit \(\tau \propto L^z\)
                to determine the dynamical exponent \(z'\).
                (Errorbars are the standard error estimated by bootstrapping.)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff algorithm. At low temperatures it flips nearly every
    spin in every step, thus the correlation drops to zero after one sweep.
    (Note that this is not the only explanation for the course of \(\tau\).
    The parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.)
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\), hence \(\tau \approx 1\) at \(T_{c}\).
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law \(\tau \propto L^z\), which is
    the expected behavior of a dynamical exponent \(z\) as mentioned in
    Sec.\ \ref{sssec:eqtime}.
    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
    not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
    for the Wolff cluster algorithm. On the one hand the number of sweeps
    in which \(\tau\) is measured in this thesis are more than a standard
    Metropolis sweep to which \(z\) normally corresponds, because each sweep
    alongside the \(N\) Metropolis flips also a cluster of \(\ge 1\) spin is
    flipped. On the other hand the \(\tau\) used for the fit are not the
    \(\tau\) at \(T_{c}\) but the maximum \(\tau\) of all \(T\).
    Nevertheless it is interesting, that it obeys a power law
    \(\tau \propto L^{z'}\). This suggests that \(\xi \gtrsim L\)
    is satisfied at the temperature of maximum \(\tau\), which is plausible,
    because the peak in Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
    is near \(T_{c}\).\\
    Anyhow, Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
    proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
    This is of course only a rough analysis of existing data which was
    generated for another purpose. For a more in depth inspection, one
    would perform the simulation at the critical point, which will be
    determined in the next sections.

\subsection{Finite Size Effects}
\label{ssec:finitesize}
    The aim of this thesis is to find the critical temperature \(T_c\)
    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean magnetization \(\avg{|m|}\) of
    the system will show a steep decline to zero and the susceptibility
    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. In Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
    it is easy to see that the steep decline of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\) (here with a RNG).
    \begin{figure}[htbp]
        \centering
        \subfigure[Dependence of the Phase Transition on $\sigma$][]
        {
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        }
        \subfigure[Example for Finite Size Effects][]
        {
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        }
        \caption[Phase Transition and Finite Size Effects]
        {
            \subref{sfig:smeared_out:meanM_L} Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying RNG with $L=128$. The position of the slope,
            and hence the critical temperature, moves to lower temperatures
            with increasing \(\sigma\)\\
            \subref{sfig:smeared_out:meanM} Effects of different system
            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
            The \(L=16\) curve is much less steep than the \(L=128\) curve.
        }
        \label{fig:smeared_out}
    \end{figure}\\
    In the shown plots there occurs no steep decline to zero, but a
    smooth decline. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
    systems, hence no computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finte size effects}.
    These finite size effects cause a "smearing out" of the phase
    transition. This is stronger for smaller system sizes, as is visible
    in Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[p. 232ff]{NewmanBarkema1999}, which also yield the critical
    exponents. This will be performed in the next section.
    Though there is an easier approach, which yields comparable precise
    values for \(T_{c}\) in a much faster and more robust way, which is
    presented in Sec.\ \ref{ssec:binderIntersections}.

@@

    As the name critical \emph{exponent} suggests, the curve progression

@@

    point, as in both examples above. But this is not imperative.

@@

    or the coupling constant \(J\) \cite{NewmanBarkema1999} of the lattice,
    therefore they should also be independent of \(\sigma\). But they are

@@

    critical exponents are not influenced by an random lattice.

@@

    the method works. For a more in depth explanation look at \cite{Norrenbrock2011} or \cite{NewmanBarkema1999}.

@@

    shows the collapse for the mean magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\),

@@

    Also the collapse of the binder cumulant as mentioned before and shown
    in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}

@@

    Therefore it is sufficient to take a few samples to test if the

@@

    examined limit of an random lattice \(\sigma \gtrsim 1\) are natural

@@

    The other \(\sigma\) are chosen to represent regions, where the behavior of

@@

            \bottomrule
        \end{tabular}
        \caption[Critical Exponents for Different $\sigma$]{
            Critical exponents for different $\sigma$. A finite size
            scaling analysis was performed to determine the critical
            exponents \(\beta, \gamma, \nu\) and the critical temperature
            \(T_c\). The errors for \(beta\) and \(\gamma\) are estimates
            by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
            \(\nu\) and \(T_c\) are the standard deviation of three obtained
            values through different collapses.
        }
        \label{tab:critExp}
    \end{table}\\
    As can be seen in Tab.\ \ref{tab:critExp}, most values
    are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
    agreement with the known value. Especially \(\nu\) and \(\gamma\)
    are always in very good agreement with their exact values. Besides the
    good agreement of the by data collapse obtained values of \(\nu\) and \(\gamma\),
    the ratio \(\frac{\gamma}{\nu}\) is also determined by fitting the maxima of
    the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
    Because there were many measurements in the vicinity of \(T_c\)
    (c.f.\ Fig.\ \ref{sfig:gettingCrit:s_1_sus}), it should give a
    reasonable estimate to take their maximum, without the need to
    interpolate.
    The results are displayed in Fig.\ \ref{fig:susCrossCheck}. The ratios
    determined by this method confirm the values obtained by collapse.
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:susCrossCheck:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNGgammaBySus}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:susCrossCheck:GG}
            \includegraphics[width=0.45\textwidth]{plots/GGgammaBySus}
        }
        \caption[Alternative Way Determining $\gamma / \nu$]
        {
            Cross checking the ratio critical exponents $\gamma$ and $\nu$ for
                \subref{sfig:susCrossCheck:RNG} the RNG at $\sigma \in \{0.0, 1.0\}$ and
                \subref{sfig:susCrossCheck:GG} the GG at $\sigma \in \{0.0, 0.3\}$.
            The plotted values are the maxima of all measured \(\chi\).
            Dotted lines are power law fits \(aL^\frac{\gamma}{\nu}\).
        }
        \label{fig:susCrossCheck}
    \end{figure}\\
    Despite the very good results for \(\nu\) and \(\gamma\), most of the
    \(\beta\) seem to be a bit too big -- especially for the RNG -- but
    they are close enough to the expectations to be consistent. At least
    the expectations are always within two times the uncertainty.
    Maybe their deviations can be explained by the fact that small
    systems (\(L=32,64\)) were used for the analysis, and no corrections
    to scaling terms were considered.
    Anyway, two critical exponents are sufficient to determine the
    universality class \cite[p. 145]{Katzgraber2011}. Therefore
    the Ising model on a proximity graph is for every \(\sigma\) in the
    same universality class as the square lattice Ising ferromagnet.

@@

    Though if one is just interested in the critical temperature, an

@@

    analytical course of the curve is not known, and hence has

@@

    As an example take Fig.\ \ref{fig:gettingCrit:binder_fit_s_0}.

@@

    are averaged and the standard error is calculated. In this case one

@@

    compared. In the following figures, the RNG will always be on the

@@

            0.00 & 2.2690(2)& 2.2689(7)& 2.2689(2)& 2.2687(5\\

@@

    of \(T_c\) on the GG. To understand that, one has to

@@

    which is necessary to flip a spins down which neighbors spins are up,

@@

    the critical temperature \(T_c\) but it is not a trivial one.

@@

        \caption[Critical Temperature Normalized by Degree of the Graph]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the RNG and
            \subref{sfig:deg:GG} the GG.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the RNG and
            \subref{sfig:Tc_norm_deg:GG} the GG.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    To understand the jump of \(T_c\), it seems to be necessary to
    understand the jump of \(K\), which is easily explained
    by the definition of the GG and its aftereffects for
    the transition from \(\sigma = 0\). Visible in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears. This process is sketched in
    Fig.\ \ref{fig:GGEdge}
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the Lunes][]{
            \label{sfig:GGEdge:before}
            \input{images/GGEdgeBefore}
        }
        \subfigure[RNG example][]{
            \label{sfig:GGEdge:after}
            \input{images/GGEdgeAfter}
        }
        \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
        {
            \subref{sfig:GGEdge:before} The edge across does not exist,
            because the other two nodes are on the edge of the lune.
            \subref{sfig:GGEdge:after} Moving one node slightly into the
            square, causes the lune to get smaller, hence no other nodes
            are inside or on the edge of the lune anymore and the edge
            appears.
        }
        \label{fig:GGEdge}
    \end{figure}\\
    Further the increase of \(T_c\) on the GG can be made plausible.
    %~ Though it is not removed by the normalization, it is reduced.
    Also the maximum of the \(K\) is at the same \(\sigma\), as the maximum
    of \(T_c\). So while displacing the nodes, there arise more edges
    than edges are vanishing until \(\sigma \approx 0.15\) is reached.
    Then more edges disappear, than appear at further displacement. This
    is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
    \begin{figure}[htbp]
        \subfigure[][$\sigma = 0.00$]
        {
            \label{sfig:GG_sigma:0.00}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][$\sigma = 0.01$]
        {
            \label{sfig:GG_sigma:0.01}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
        }

@@

        \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the RNG and
            \subref{sfig:sumJ:GG} the GG.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the RNG and
            \subref{sfig:Tc_normJ:GG} the GG.
        }
        \label{fig:TcJ}
    \end{figure}\\
    Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
    to be a linear connection between \(J\) and \(T_c\), the best guess
    is a linear connection, because this model is derived from the
    square lattice, where the connection is linear. Therefore, one
    normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the GG arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\).
    %~ This is a strong hint, that the change of the \(T_c\) with changing
    %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
    %~ expected conclusion.\\
    Moreover the forms of both curves are quite similar, but the
    one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
    disorder has little influence on this normalized critical temperature.
    Also both graph types have a steep decline after the plateau before
    they approach an asymptotic limit for \(\sigma \gg 1\).\\

>>>>

            rounded up and determined as the maximum over all \(\sigma\).

@@

    are omitted in the following for the sake of simplicity so that the

@@

    error estimate can be achieved by simple bootstrapping. Nevertheless, one has

@@

    by gnuplot. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
    source plotting program used for all plots and fits in this thesis.

\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
\label{ssec:results:autocorr}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) is given to illustrate the benefits
    of the used Wolff cluster algorithm.\\
    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at
    \(\sigma=0\) is plotted. Note that these are the unrounded values
    of Tab.\ \ref{tab:tauAndTeq}.
    \begin{figure}[htbp]
        \centering
        \subfigure[in Dependence on the Temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in Dependence on the System Size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The Autocorrelation Time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$. Plotted on
                double logarithmic axis with a power law fit \(\tau \propto L^z\)
                to determine the dynamical exponent \(z'\).
                (Errorbars are the standard error estimated by bootstrapping.)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff algorithm. At low temperatures it flips nearly every
    spin in every step, thus the correlation drops to zero after one sweep.
    (Note that this is not the only explanation for the course of \(\tau\).
    The parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.)
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\), hence \(\tau \approx 1\) at \(T_{c}\).
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law \(\tau \propto L^z\), which is
    the expected behavior of a dynamical exponent \(z\) as mentioned in
    Sec.\ \ref{sssec:eqtime}.
    In Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\). Note that the exponent \(z'=0.64(2)\) determined by this plot is
    not comparable to the known critical exponent \(z=0.25\) \cite{NewmanBarkema1999}
    for the Wolff cluster algorithm. On the one hand the number of sweeps,
    in which \(\tau\) is measured in this thesis, are more than a standard
    Metropolis sweep to which \(z\) normally corresponds, because each sweep
    alongside the \(N\) Metropolis flips also a cluster of \(\ge 1\) spin is
    flipped. On the other hand the \(\tau\) used for the fit are not the
    \(\tau\) at \(T_{c}\) but the maximum \(\tau\) of all \(T\).
    Nevertheless it is interesting, that it obeys a power law
    \(\tau \propto L^{z'}\). This suggests that \(\xi \gtrsim L\)
    is satisfied at the temperature of maximum \(\tau\), which is plausible,
    because the peak in Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw}
    is near \(T_{c}\).\\
    Anyhow, Fig.\ \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} alone
    proofs the effectiveness of the Wolff cluster algorithm at criticality.\\
    This is of course only a rough analysis of existing data which was
    generated for another purpose. For a more detailed inspection, one
    would perform the simulation at the critical point, which will be
    determined in the next sections.

\subsection{Finite Size Effects}
\label{ssec:finitesize}
    The aim of this thesis is to find the critical temperature \(T_c\)
    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean magnetization \(\avg{|m|}\) of
    the system will show a steep decline to zero and the susceptibility
    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. In Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM_L}
    it is easy to see that the steep decline of \(\avg{|m|}\)
    occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\) (here with a RNG).
    \begin{figure}[htbp]
        \centering
        \subfigure[Dependence of the Phase Transition on $\sigma$][]
        {
            \label{sfig:smeared_out:meanM_L}
            \includegraphics[width=0.45\textwidth]{plots/Mean_M_L_128}
        }
        \subfigure[Example for Finite Size Effects][]
        {
            \label{sfig:smeared_out:meanM}
            \includegraphics[width=0.45\textwidth]{plots/meanM}
        }
        \caption[Phase Transition and Finite Size Effects]
        {
            \subref{sfig:smeared_out:meanM_L} Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying RNG with $L=128$. The position of the slope,
            and hence the critical temperature, moves to lower temperatures
            with increasing \(\sigma\)\\
            \subref{sfig:smeared_out:meanM} Effects of different system
            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.
            The \(L=16\) curve is much less steep than the \(L=128\) curve.
        }
        \label{fig:smeared_out}
    \end{figure}\\
    In the shown plots there occurs no steep decline to zero, but a
    smooth one. \(\avg{\abs{m}}(T_c) = 0\) is only present in infinite
    systems, hence no computer simulation will show the exact behavior in the
    thermodynamic limit. It will always show some \emph{finte size effects}.
    These finite size effects cause a "smearing out" of the phase
    transition. This is stronger for smaller system sizes, as shown
    in Fig.\ \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\
    Despite of this one can obtain \(T_c\) by finite size scaling
    methods \cite[p. 232ff]{NewmanBarkema1999}, which also yield the critical
    exponents. This will be performed in the next section.
    Though there is an easier approach, which yields comparable precise
    values for \(T_{c}\) in a much faster and more robust way, which is
    presented in Sec.\ \ref{ssec:binderIntersections}.

@@

    As the name "critical \emph{exponent}" suggests, the curve progression

@@

    point as in both examples above. But this is not imperative.

@@

    or the coupling constant \(J\) \cite{NewmanBarkema1999} of the lattice.
    Therefore they should also be independent of \(\sigma\). But they are

@@

    critical exponents are not influenced by a random lattice.

@@

    the method works. For a more detailed explanation look at \cite{Norrenbrock2011} or \cite{NewmanBarkema1999}.

@@

    show the collapse for the mean magnetization per site \(\avg{\abs{m}}\) for \(\sigma=1\)

@@

    Also the collapse of the binder cumulant, as mentioned before and shown
    in Fig.\ \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0},

@@

    Therefore it is sufficient to take a few samples to test, if the

@@

    examined limit of a random lattice \(\sigma \gtrsim 1\) are natural

@@

    The other \(\sigma\) are chosen to represent regions where the behavior of

@@

            \bottomrule
        \end{tabular}
        \caption[Critical Exponents for Different $\sigma$]{
            Critical exponents for different $\sigma$. A finite size
            scaling analysis was performed to determine the critical
            exponents \(\beta, \gamma, \nu\) and the critical temperature
            \(T_c\). The errors for \(beta\) and \(\gamma\) are estimates
            by \texttt{autoscale.py} \cite{autoscale2009}. The errors of
            \(\nu\) and \(T_c\) are the standard deviation of three obtained
            values through different collapses.
        }
        \label{tab:critExp}
    \end{table}\\
    According to Tab.\ \ref{tab:critExp}, most values
    are matching the expectations. \(T_c\) for \(\sigma = 0\) is in good
    agreement with the known value. Especially \(\nu\) and \(\gamma\)
    are always in very good agreement with their exact values. Besides the
    good agreement of the by data collapse obtained values of \(\nu\) and \(\gamma\),
    the ratio \(\frac{\gamma}{\nu}\) is also determined by fitting the maxima of
    the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
    Because there were many measurements in the vicinity of \(T_c\)
    (c.f.\ Fig.\ \ref{sfig:gettingCrit:s_1_sus}), it should give a
    reasonable estimate to take their maximum, without the need to
    interpolate.
    The results are displayed in Fig.\ \ref{fig:susCrossCheck}. The ratios
    determined by this method confirm the values obtained by collapse.
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:susCrossCheck:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNGgammaBySus}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:susCrossCheck:GG}
            \includegraphics[width=0.45\textwidth]{plots/GGgammaBySus}
        }
        \caption[Alternative Way Determining $\gamma / \nu$]
        {
            Cross checking the ratio critical exponents $\gamma$ and $\nu$ for
                \subref{sfig:susCrossCheck:RNG} the RNG at $\sigma \in \{0.0, 1.0\}$ and
                \subref{sfig:susCrossCheck:GG} the GG at $\sigma \in \{0.0, 0.3\}$.
            The plotted values are the maxima of all measured \(\chi\).
            Dotted lines are power law fits \(aL^\frac{\gamma}{\nu}\).
        }
        \label{fig:susCrossCheck}
    \end{figure}\\
    Despite the very good results for \(\nu\) and \(\gamma\), most of the
    \(\beta\) seem to be a bit too big -- especially for the RNG -- but
    they are close enough to the expectations to be consistent. At least
    the expectations are always within two times the uncertainty.
    Maybe their deviations can be explained by the fact that small
    systems (\(L=32,64\)) were used for the analysis and no corrections
    to scaling terms were considered.
    Anyway, two critical exponents are sufficient to determine the
    universality class \cite[p. 145]{Katzgraber2011}. Therefore,
    the Ising model on a proximity graph is for every \(\sigma\) in the
    same universality class as the square lattice Ising ferromagnet.

@@

    Though, if one is just interested in the critical temperature, an

@@

    analytical course of the curve is not known and hence has

@@

    Take Fig.\ \ref{fig:gettingCrit:binder_fit_s_0} as an example.

@@

    are averaged and the standard error is calculated. In this case, one

@@

    compared. In the following figures the RNG will always be on the

@@

            0.00 & 2.2690(2)& 2.2689(7)& 2.2689(2)& 2.2687(5)\\

@@

    of \(T_c\) on the GG. To understand that one has to

@@

    which is necessary to flip a spins down whose neighbors spins are up,

@@

    the critical temperature \(T_c\), but it is not a trivial one.

@@

        \caption[Critical Temperature Normalized by Degree of the Graph]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the RNG and
            \subref{sfig:deg:GG} the GG.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the RNG and
            \subref{sfig:Tc_norm_deg:GG} the GG.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    To understand the jump of \(T_c\) it seems to be necessary to
    understand the jump of \(K\), which is easily explained
    by the definition of the GG and its aftereffects for
    the transition from \(\sigma = 0\). Visible in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.00}\subref{sfig:GG_sigma:0.01}
    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears. This process is sketched in
    Fig.\ \ref{fig:GGEdge}
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the Lunes][]{
            \label{sfig:GGEdge:before}
            \input{images/GGEdgeBefore}
        }
        \subfigure[RNG example][]{
            \label{sfig:GGEdge:after}
            \input{images/GGEdgeAfter}
        }
        \caption[Sketch why Many New Edges Arise at the Transition from $\sigma = 0$ to $\sigma > 0$]
        {
            \subref{sfig:GGEdge:before} The edge across does not exist,
            because the other two nodes are on the edge of the lune.
            \subref{sfig:GGEdge:after} Moving one node slightly into the
            square, causes the lune to get smaller, hence no other nodes
            are inside or on the edge of the lune anymore and the edge
            appears.
        }
        \label{fig:GGEdge}
    \end{figure}\\
    Further the increase of \(T_c\) on the GG can be made plausible.
    %~ Though it is not removed by the normalization, it is reduced.
    Also the maximum of the \(K\) is at the same \(\sigma\), as the maximum
    of \(T_c\). So while displacing the nodes, there arise more edges
    than edges are vanishing until \(\sigma \approx 0.15\) is reached.
    Then more edges disappear, than appear at further displacement. This
    is not an obvious effect, but can be seen in Fig.\ \ref{fig:GG_sigma}\subref{sfig:GG_sigma:0.09}\subref{sfig:GG_sigma:0.15}\subref{sfig:GG_sigma:0.21}
    \begin{figure}[htbp]
        \subfigure[][$\sigma = 0.00$]
        {
            \label{sfig:GG_sigma:0.00}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][$\sigma = 0.01$]
        {
            \label{sfig:GG_sigma:0.01}
            \includegraphics[width=0.30\textwidth]{images/GG/sigma_g0}
        }

@@

        \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the RNG and
            \subref{sfig:sumJ:GG} the GG.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the RNG and
            \subref{sfig:Tc_normJ:GG} the GG.
        }
        \label{fig:TcJ}
    \end{figure}\\
    Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
    to be a linear connection between \(J\) and \(T_c\), the best guess
    is a linear connection, because this model is derived from the
    square lattice, where the connection is linear. Therefore, one
    normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the GG arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\).
    %~ This is a strong hint, that the change of the \(T_c\) with changing
    %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
    %~ expected conclusion.\\
    Moreover the forms of both curves are quite similar, but the
    one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
    Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
    is that small disorder has little influence on this normalized critical
    temperature.
    Also both graph types have a steep decline after the plateau before
    they approach an asymptotic limit for \(\sigma \gg 1\).\\

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g_c\)
    depends strongly on boundary conditions but only weakly on the lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses another definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match its definition in this thesis.}.
    Because the analysis of Sec.\ \ref{ssec:binderIntersections}
    yields \(g_c\) anyway, it is easy to check the consistency and
    behavior of \(g_c\) in the disordered Ising model.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a RNG][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a GG][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder Cumulant at the Critical Point $g_c$]
        {
            Values of the Binder cumulant at the critical point \(g_c\)
            for\\
            \subref{sfig:TcG:RNG} a RNG and\\
            \subref{sfig:TcG:GG} a GG for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
    Considering both plots in Fig.\ \ref{fig:TcG}, \(g_c\) is for low
    \(\sigma\) obviously always bigger than the known value. Though the
    deviations are only very small. Perhaps this overestimation is caused
    by the cubic spline interpolation used to acquire these \(g_c\) values.
    For bigger \(\sigma\) the uncertainty gets greater, but the values
    do only differ by a few percent, hence even the big disorder and
    definition of nearest neighbors via a proximity graph does not change
    \(g_c\) much. Though it is mentioned in \cite{BinderValue} that the
    lattice structure has a minor effect on \(g_c\), the uncertainty of
    \(g_c\) is too big, to show it. For a more exact analysis, new
    Monte Carlo simulations at \(T_c\) would be needed. But this is
    beyond the scope of this thesis. Anyway, the results are the expected
    behavior, because no major deviations from the value of \(g_c\) at
    \(\sigma = 0\) occur at larger \(\sigma\).
